Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-02-18 main.tex
FONDA ack

\subsubsection*{Acknowledgements}
Funding acknowledgement suppressed to preserve anonymity.
%This work is partially supported by Collaborative Research Center (CRC) 1404 FONDA
%–- Foundations of Workflows for Large-Scale Scientific Data Analysis, which is funded
%by German Research Foundation (DFG).
% TODO: include FONDA ack in final version

>>>>

\subsubsection*{Acknowledgements}
This work is partially supported by Collaborative Research Center (CRC) 1404 FONDA
–- Foundations of Workflows for Large-Scale Scientific Data Analysis, which is funded
by German Research Foundation (DFG).
